Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-01-31 paper/experiments.tex
Paper update

For all functions except the two 10D functions, we set the number of initial
random sampling to $N_{init} = 20$ and the number of iterations to 45. Batch
size are set to $B = 1 $ and $B = 4$ respectively, the total number of function
evaluations is $N_{init} + B \times iter$. For the 10D ackley and 10D
rosenbrock functions, we set the number of initial sampling to $N_{init} = 100$
and the number of iterations is fixed to 175. The experiments were repeated for
ten times to average the random fluctuations.

@@

As can be seen in Figure~\ref{fig:CovPlotBenchmark}, the MACE strategy is
competitive in both sequential and batch setting. The qKG method performed not
good for these benchmark functions, in some functions, it was even outperformed
by the sequential EI and LCB.

Other algorithms gave acceptable solutions, while the MACE algorithm are
usually the best or second best algorithms for these benchmark functions.

>>>>

For all functions except the two 10D functions, we set the number of initial
random sampling to $N_{init} = 20$ and the number of iterations to 45. Batch
size are set to $B = 4$, the total number of function evaluations is $N_{init}
+ B \times iter$. For the 10D ackley and 10D rosenbrock functions, we set the
number of initial sampling to $N_{init} = 100$ and the number of iterations is
fixed to 175. The experiments were repeated for ten times to average the random
fluctuations. The MACE, EI and LCB acquisition functions are also tested with
$B = 1$.

@@

As can be seen in Figure~\ref{fig:CovPlotBenchmark}, for lower dimensional
functions, the MACE algorithm, BLCB algorithm and the EI-LP algorithm are among
the best algorithm, the have quite similar convergence rate, while the qEI and
qKG were outperformed by the above three algorithms. For the 10D ackley and 10D
rosenbrock functions, the MACE have the fastest convergence rate.
